Realizability-Preserving DG-IMEX Method for the Two-Moment Model of Fermion Transport \tnoteref{support}

### 2018-05-29 Documents/M1/realizableFermionicM1/sections/imex.tex
Added 'Absolute Stability' subsectionto IMEX section.

>>>>

\subsection{Absolute Stability}

The absolute stabilities of the proposed IMEX schemes,  PA2+ and PARSD (given in \ref{app:butcherTables}), are analyzed following form \cite{hu_etal_2017}.
An IMEX scheme can be written as $\vect{u}^{n+1} =P(z_1,z_2)\vect{u}^{n}$, where $P(z_1,z_2)$ is the amplification factor of the scheme, $z_1 = x +iy$ corresponds to the explicit part of the scheme, and $z_2 < 0$ corresponds to the implicit part.
The absolute stability requires $|P|\leq 1$. 
The stability regions of PA2+ and PARSD are plotted in Figure~\ref{fig:AbsoluteStability}.
As can be seen form the figure, the absolute stability region increase with $|z_2|$ increasing for both schemes.
Thus, a time step that satisfies the absolute stability for the explicit part of the IMEX scheme, $|z_2| = 0$, fulfill the stability requirement for the whole IMEX scheme, $|z_2| \geq 0$. 
This conclusion is valid for all PARSD $\epsilon\in [0,0.5)$.
\begin{figure}[h]
  \centering
  \begin{tabular}{cc}
    \includegraphics[width=0.5\textwidth]{figures/AbsoluteStabilityPARSD}
    \includegraphics[width=0.5\textwidth]{figures/AbsoluteStabilityPA2+}
  \end{tabular}
   \caption{Boundary of the absolute stability region for different values of $z_2$. Left: PARSD with $\epsilon = 0.1$. Right: PA2+.}
  \label{fig:AbsoluteStability}
\end{figure}
